\chapter{Preface}

A Chef Style DevOps Kung-fu implementation, inspired
in the Adam Jacob keynote from Chefconf 2015. A practical
to work with infrastructure automaion, continuous delivery,
continuous deployments and the platform maintenance life cyle.

The source code of this book is hosted in \href{https://github.com/carlosdcg/chefbyexample_book}{Github},
everyone can fork and make pull requests; you are all invited.

\section{What is DevOps?}

There isn’t an agreed definition for DevOps yet.
DevOps is a cultural and professional movement, focused on
how we build and operate high velocity organizations, born
from the experience of its practitioners. Is a
unique approach, based in previous experience and focused on customers.

\begin{itemize}
\item Principles (Universal)

\begin{itemize}
\item Based on prioritize people over products over companies.
\item Design for the safety, contentment, knowledge and freedom of both your peers and your customers.
\item Eliminate non-value-added actions and processes.
\item Continuously improve your processes.
\item Adapt to needs.
\item Small improvements over the time.
\item Fail faster to learn faster. Be calm, fix things and improve your processes.
\item Workflows automation.
\item Diversity, gets feedback, have different opinions, argue, make demonstrations on your points of view.
\item Demo all the things you have or you are working in.
\item Be the owner of your work, love your work, and find reasons to do your work.
\item Improve and do things right even if is hard (At first).
\item Make decisions based on your experience and proof your point of view.
\end{itemize}
\item Forms (Shared)
\item Applications (Unique)
\end{itemize}

\section{What this book covers}

\section{What you need for this book}

\section{Who this book is for}

\section{Conventions}